A recipe for extremely reproducible enrichment analysis (and why we need it)

### 2023-05-02 manuscript.Rmd
minor edits

* Protocol: protocols.io

* Boilerplate code: https://github.com/markziemann/enrichment_recipe

>>>>

* Protocol: https://github.com/markziemann/enrichment_recipe/blob/main/docs/guide_for_linux_users_with_docker.md
A final version will be deposited to protocols.io.

* Code repository including template Dockerfile and Rmarkdown script: https://github.com/markziemann/enrichment_recipe
